Effect of character correlation

### 2019-04-23 Analysis/02-EffectCorrelationFullResults.Rmd
added combined results test tables

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide', warning = FALSE}
## Labels
labels_wx <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
make.xtable(wx_RF_best, caption = captions_wx[1], label = labels_wx[1], path = "../Writing/Tables/")
make.xtable(wx_Tr_best, caption = captions_wx[2], label = labels_wx[2], path = "../Writing/Tables/")
make.xtable(wx_RF_null, caption = captions_wx[3], label = labels_wx[3], path = "../Writing/Tables/")
make.xtable(wx_Tr_null, caption = captions_wx[4], label = labels_wx[4], path = "../Writing/Tables/")
```

>>>>

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide', warning = FALSE}
## Labels
labels_wx <- paste0("Full_Tab_Bayesian_WX", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Tables
## Bayesians
make.xtable(wx_RF_best[1:9,], caption = captions_wx[1], label = labels_wx[1], path = "../Writing/Tables/")
make.xtable(wx_Tr_best[1:9,], caption = captions_wx[2], label = labels_wx[2], path = "../Writing/Tables/")
make.xtable(wx_RF_null[1:9,], caption = captions_wx[3], label = labels_wx[3], path = "../Writing/Tables/")
make.xtable(wx_Tr_null[1:9,], caption = captions_wx[4], label = labels_wx[4], path = "../Writing/Tables/")

labels_wx <- paste0("Full_Tab_Parsimony_WX", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

## Parsimonies
make.xtable(wx_RF_best[10:18,], caption = captions_wx[1], label = labels_wx[1], path = "../Writing/Tables/")
make.xtable(wx_Tr_best[10:18,], caption = captions_wx[2], label = labels_wx[2], path = "../Writing/Tables/")
make.xtable(wx_RF_null[10:18,], caption = captions_wx[3], label = labels_wx[3], path = "../Writing/Tables/")
make.xtable(wx_Tr_null[10:18,], caption = captions_wx[4], label = labels_wx[4], path = "../Writing/Tables/")
```
